We describe the scenario that we will use for our analysis and
discussion.
%
\eMcomm[tbc]{}


\hsl[CAS = CPS?\\ \textbf{If}
CAS $\neq$ CPS
\\\textbf{then}
\cite{pt21icsa} not designed for CAS AND \cite{itt20} not designed for changes
\\
\textbf{else} ???
\\
\textbf{fi}]

We consider the analysis presented in~\cite{pt21icsa} to assess the
performance characteristics of architectural patterns in a
cyber-physical system in presence of dynamic physical changes.
%
The analysis conducted in this paper shows that by considering a set
of models it is possible to measure the impact of architectural
patterns and dynamic space changes on the performance of
cyber-physical systems.
%
This type of analysis suggests that in this domain it is useful to
factor performance in at design time.
%
The approach proposed in~\cite{pt21icsa} is new and it hinges on
generalised stochastic petri nets (GSPN)~\cite{gspn}.

\eMcomm[weak]{In this paper we apply such approach to CAS and study.}
%
Also, we study the relative merits of the approach in~\cite{pt21icsa}
and the one proposed in~\cite{itt20} advocating the combination of
behavioural specifications and queuing networks~\cite{qn} for
performance analysis of CAS.
%
More precisely we address the following two research questions:
\begin{description}
\item[RQ1] To what extent the approaches in~\cite{pt21icsa}
  and in~\cite{itt20} support performance-aware design of CAS?
\item[RQ2] How the features of the approaches in~\cite{pt21icsa}
  and in~\cite{itt20} compare?
\end{description}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
